
\chapter*{Appendix A: Quick Reference Card}
\addcontentsline{toc}{chapter}{Appendix A: Quick Reference Card}

\section*{The Seven Dimensions at a Glance}

\begin{itemize}
\item \textbf{Θ (Theta)} – Logic / Collapse  
Manages superposition and collapse of logical states.

\item \textbf{λ (Lambda)} – Trace / Memory  
Tracks historical structure and collapse history.

\item \textbf{η (Eta)} – Entropy / Variance  
Encodes systemic disorder and directional flow.

\item \textbf{κ (Kappa)} – Curvature / Structure  
Defines symbolic landscape and descent gradients.

\item \textbf{ϕ (Phi)} – Phase / Synchronization  
Coordinates timing and cyclic interaction between systems.

\item \textbf{ψ (Psi)} – Identity / Persistence  
Preserves symbolic self across transitions.

\item \textbf{χ (Chi)} – Interference / Coupling  
Tracks entanglement, interaction, and external influence.
\end{itemize}

\section*{Common Structural Patterns}

\begin{itemize}
\item $\Theta$ collapse $\Rightarrow$ λ trace grows
\item λ overflow $\Rightarrow$ η entropy increases
\item η > threshold $\Rightarrow$ Θ collapse required
\item κ curvature singular $\Rightarrow$ ψ test identity
\item ϕ alignment $\Rightarrow$ χ constructive interference
\end{itemize}

\section*{Structural State Evolution}

\begin{verbatim}
while not converged:
    check_coherence()
    propose_updates()
    validate_constraints()
    apply_changes()
    project_if_needed()
\end{verbatim}

\section*{Collapse Limit Theorem}
\[
c = P_4(c^*) \quad \text{where} \quad c^* = \left( \max_{\sigma_i} \Delta t_{\text{collapse}}(\sigma_i) \right)^{-1}
\]

\section*{Symbolic State}

\[
\Psi_7 = (\Theta, \lambda, \eta, \kappa, \phi, \psi, \chi)
\]

Each symbol is an operator, not a variable. Together they define structural evolution.

