
\section{Instability-Adaptive Function Expansion: A Structural Extension of Taylor Series}

\subsection{The Classical Limitation}

The Taylor series assumes that a function is locally well-behaved and infinitely differentiable at a point $x_0$:
\[
f(x) = \sum_{n=0}^{\infty} \frac{f^{(n)}(x_0)}{n!} (x - x_0)^n
\]
But many physically or symbolically important functions violate this assumption. Consider:
\[
f(x) = \sum_{n=0}^{\infty} (-1)^n n! x^n
\]
This series diverges for all $x \neq 0$. Still, we know this function encodes meaningful structure. So why can’t the expansion reflect that?

\subsection{Structural Insight: The Instability Field $\lambda_n(x)$}

Each derivative term $f^{(n)}(x)$ carries a hidden collapse signature: how unstable it is in its contribution. We define:
\[
\lambda_n(x) = \left| \frac{d}{dx} \log \left| f^{(n)}(x) \right| \right|
\]
Large $\lambda_n(x)$ implies high sensitivity—i.e., symbolic instability or curvature tension in the system’s structure.

\subsection{Collapse-Aware Modulation via $\phi_n(x)$}

Rather than discard these unstable terms, we stabilize them by introducing a modulation factor:
\[
\phi_n(x) = \exp(-\alpha \cdot \lambda_n(x))
\]
This acts like an entropy-dampening envelope or symbolic trace corrector. Terms that are stable (low $\lambda_n$) are mostly preserved; unstable terms are suppressed.

\subsection{The Modified Expansion}

The resulting collapse-aware series becomes:
\[
\tilde{f}(x) = \sum_{n=0}^\infty \phi_n(x) \cdot \frac{f^{(n)}(x_0)}{n!} (x - x_0)^n
\]

This series:
\begin{itemize}
\item Converges in regions where the classical series fails
\item Preserves the symbolic trace of the function
\item Adjusts dynamically to local instability
\end{itemize}

\input{Taylor_Collapse_Figure_Insert.tex}

\subsection{Syn/GL Interpretation}

In Syn/GL terms:
\begin{itemize}
\item $\lambda$ detects entropy-explosive trace divergence
\item $\phi_n(x)$ represents symbolic entropy control ($\eta$-adaptive modulation)
\item The series modulates collapse based on local structural curvature ($\kappa$)
\item This avoids destructive $\Theta$-collapse while maintaining $\lambda$-trace
\end{itemize}

This is not an approximation trick. It’s symbolic stability encoding.

